\label{sec:intro}
\section{Introduction}

In the current cosmological paradigm about 23\% of the energy and matter
content of the Universe is dark matter and $1\%$ is baryonic matter.
Dark matter particles collapse gravitationally to form large structures
knows as halos. In the context of the $\Lambda CDM$, where structure grows
hierarchically, baryonic matter accumulates within dark matter halos,
allowing galaxies to form and evolve. Therefore, galaxy formation processes
are strongly related with the evolution of dark matter halos. In particular,
the morphology, kinematics, dynamics of galaxies disks and satellite
remnants of hierarchical processes such as streams are useful observables
that help to constrain halos` properties like their total mass, density and shape.

%nderstanding the nature of dark matter is one of the most important challenges in
%strophysics. Astrophysical constraints are useful to test the predictions
%f the dark matter nature. %(modify last sentence)

Crucial theoretical efforts have been made to model the properties of dark
matter halos. \citep{Hernquist90}, Plummer, Dehnen, derived analytical expressions for
the density profiles of spherical dark matter halos. Using cosmological
simulations \citep{Navarro96, Navarro97} found an analytical expression for spherical
dark matter profiles in a cold dark matter universe. 

Nevertheless accretion of subhalos to the halos is an asymmetric
process that depends on the large scale structure \citep{Tormen97,Colberg99},
therefore, the structure of halos should not be spherical.
These have been found in cosmological N-body simulations \citep{Barnes87,
Frenk88, Dubinski91, Warren92, Tormen97, Thomas98} and in more recent
simulations with higher resolution, all these works agree in the fact.

%he effect of baryons.

In observations the shape of dark matter halos might be derived from
X-rays clusters, gravitational lensing, shapes of galactic disks 
observations and in the spatial distribution of galaxies in groups.

% MW scenario

In the Milky Way close satellite galaxies and globular clusters that orbit 
around can trace the mass and shape of the halo if the position, line of
sight velocities and tangential velocities are known. Such observations
have been made for several objects, allowing different
research groups to constrain the mass of the Milky Way, nevertheless, there is not a consistent
agreement yet. %(Put an example)

Due to the dynamical friction satellite galaxies and globular clusters
will decay over time. During this process the satellite will be
destroyed leaving tidal streams as tracers of this process
\citep{Toomre72, LyndenBell95, Johnston96}. These streams are observed in the Milky Way
, The first disrupting satellite galaxy observed inside the Milky Way halo was the Sagittarius dwarf
galaxy \citep{Ibata94}. Sections of streams associated with Sagittarius were
observed in (ivezic00, yanny00, ibata01b).
These streams segments were revealed to be connected, forming a stream
spanning for more than $360°$ (majewsky03, piladiaz13, belokurov14), the stream have a width ($>20°$) (belokurov06) and it warps
for more than $360°$. The velocity space is ($>20km/s$) (koposov13)
which suggests that
the Sgr stream is dynamically hot.

\begin{table}
\begin{center}
\begin{tabular}{c c c}
\hline
\hline
Halo Shape & Author & Parameters \\
\hline
Spherical & Ibata et al 01 & \\
Spherical & Law05 & \\
Spherical & Fellhauer06 & \\
Prolate & Helmi 04 & \\
Oblate & Johnston05 & \\
Oblate & MartinezDelgado07 & \\
Triaxial & LMJ09 & \\
Triaxial & LM & \\
Oblate-Triaxial & Vera-Ciro13 & \\
\hline
\hline
\end{tabular}
\caption{Halo Shape models derived from streams.\label{tab:models}}
\end{center}
\end{table}


With these observations several groups have attempted to reproduce the
stream with N-body models \ref{tab:models}, founding different halo
shapes. From these models, the \citep{Law10} model has been
the more successful by reproducing the observed positions and velocities
of the stream. Nevertheless, it's halo configuration is unusual
because the major axis is perpendicular to the plane of the disk; this
configuration is not favorable for the formation of the
Milky Way Disk \citep{Debattista13}.

These disagreements motivate the use of other streams to map the halo,
recently \citep{Pearson15} used the Palomar 5 (Pal5) stream to constrain the dark
matter halo of the Milky Way. The stream is $22\degree$
long and with a width of $0.7 \degree$. The globular cluster is currently at the
apocenter of the orbit at 23.6kpc from the Sun (Dotter et al 2011). Interestingly
the potential that reproduce the morphology of Pal5 is spherical.
Recent observations of Pal5 \citep{Fritz15} also suggest a spherical
halo with $V_0 = 220 km/s$ and $V_{20kpc} = 218 km/s$. These results
are in disagreement with the \citep{Law10} model that reproduce the Sagittarius stream
and also such a halo shape is uncommon in the $\Lambda$CDM
paradigm. %\verb+ponercita+.

%New techniques are being developed with the aim of constraining the halo with multiple
%streams at different distances at the same time (Bonaca14). These techniques
%prevent the underestimation or overestimation of the halo mass.
%\textbf{why?}

However, all of the studies that constrain the dark matter halo using streams
assume a static dark matter halo. \citep{Buist15} claim that if the dark matter
halo is changing in time misalignments on the orbit of long streams could appear.
%\textbf{explain}

The Milky Way is not isolated, in fact it is interacting with a
massive satellite ~$1\times10^{11}M_{\odot}$ (\textbf{where this came
from}), the Large Magellanic Cloud (LMC),
which is in the first passage about the MW and is currently at the pericenter
of the orbit at 50Kpc from the Galactic center. Such a massive satellite inside the virial
radius ($R_{vir}\sim 261kpc$) of the Milky Way should be distorting
the it's dark matter
halo. %\textbf{Why? Compre MW rot cum, mass enclosed within 50kpc & Mass
%enclosed of LMC. Create a simple model Gomez2015, orbital barycenter
%changes. 1:4 merger}

Due to the LMC, the dark matter halo of the Milky Way might be
distorted and evolving in time. Consequently, a detailed study of the
influence of the LMC on the MW dark matter halo shape is needed. Two
main questions are addressed in this work: What are the evolving shape of the inner
(<20kpc) and outer halo (>20kpc) and what are the torques applied
to streams in the inner halo.

We use N-body simulations, which reproduce the orbital history of the
Large Magellanic Cloud around the Milky Way. In these simulations the Milky Way is modeled
using an spherical halo that is distorted by the Large Magellanic
Cloud.
In \S\ref{sec:models} we described the models used for the Large
Magellanic Cloud and
the Milky Way. In \S\ref{sec:IC} we explained how we derived our initial
conditions that reproduce the orbital history of the Large Magellanic
Cloud. In \S\ref{sec:shapes} we explained the methods used to study
the shape of the halos. In \S\ref{sec:results} we present our
results.
